Wolbachia and Two Other Microbes Nobody Cares About That Changed The World Kinda

### 2015-12-16 paper.tex
Something is broken

During the 1950s a group of scientists found that certain matching between\textit{Culex} mosquitos produced no offspring. They named this phenomenon cytoplasmic incompatibility, although they were not sure as to what the cause was.[17] It wasn't until the 1970s that cytoplasmic incompatibility was linked to\textit{Wolbachia}, when a group of scientists eliminated the\textit{Wolbachia} through antibiotics.[18]

@@

\section*{References}
\medskip
\printbibliography

>>>>

During the 1950s a group of scientists found that certain matching between\textit{Culex} mosquitos produced no offspring. They named this phenomenon cytoplasmic incompatibility, although they were not sure as to what the cause was.\cite{Wcyto_iso} It wasn't until the 1970s that cytoplasmic incompatibility was linked to\textit{Wolbachia}, when a group of scientists eliminated the\textit{Wolbachia} through antibiotics.\cite{Wcyto_cause}

@@

\section*{References}

\printbibliography
